Updated Ephemerides of the young multi-planet system V1298 Tau from TESS

### 2021-10-21 src/ms.tex
inconsistencies between overleaf and here, mybad
yus that was the problem

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.46\textwidth,trim={0.25cm 0 60cm 100cm}]{figures/TESSaperture.pdf}
\caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band. \sname is shown in the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's. There are two bight nearby sources to \sname. However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.} \label{fig:tpf}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/lightcurve.pdf}
\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color. Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (blue). Middle row: the \tess\ light curve with the stellar variability removed by our model. Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43.} 
\label{fig:transits}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\begin{center}
\includegraphics[width=0.46\textwidth,trim={0.1cm 0 50cm 80cm}]{figures/TESSaperture.pdf}
\caption{The \tess\ target pixel file (TPF) overlaid with a sky image of \sname taken with the Sloan Digital Sky Survey (SDSS) i-band. \sname is shown in the white circle; nearby sources with \tess\ magnitudes $< 14$ are marked with orange x's. There are two bight nearby sources to \sname. However, selecting the one pixel aperture (white square) encapsulates only \sname and therefore contamination from the nearby sources is negligible.} \label{fig:tpf}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images, with transits of \allplanets highlighted by color. Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (blue). Middle row: the \tess\ light curve with the stellar variability removed by our model. Bottom rows: zoomed-in regions around the visible transits during the first orbit (third row) and second orbit (last row) from \tess\ Sector 43.} 
\label{fig:transits}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
